%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Gloria del Valle Cano} \\ \vspace{0.9em}
    \small +34 635 88 68 67 · \href{mailto:glorelvalle@gmail.com}{\textcolor{Periwinkle}{glorelvalle@gmail.com}} ·
    %\href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jake}} $|$
    \href{https://github.com/glorelvalle}{\textcolor{BlueViolet}{github.com/glorelvalle}}
\end{center}

\vspace{0.5em}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MSc Data Science}{September 2021 -- \textit{Present}}
      {Autonomous University of Madrid}{}
      \resumeItemListStart
        \resumeItem{Studying advanced methods in statistics and stochastic processes, inter alia.}
        \resumeItem{Attending to elective courses such as Natural Language Processing, Deep Learning for Image and Video Classification, Bayesian Methods and Functional Methods in Machine Learning.}
    \resumeItemListEnd
    \resumeSubheading
      {BSc Computer Science Engineering}{September 2013 -- June 2021}
      {Autonomous University of Madrid}{}
      \resumeItemListStart
      \resumeItem{Studying solutions based on AI, computer security, systems administration and Big Data.}
      \resumeItem{Working in part-time jobs as sales assistant for more than 4 years (25-35 hours per week).}
      \resumeItem{Thesis: \textit{Detecting hate messages on Twitter: a study based on perfles within the social network.} [\textbf{Grade A}].}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Data Scientist}{ September 2022 -- \textit{Present}}
      {Grupo TRC)}{Madrid, Spain}
      \resumeItemListStart
        \resumeItem{}
        \resumeItem{}
        \resumeItem{}
      \resumeItemListEnd

      \resumeSubheading
      {Research Assistant}{ January 2022 -- September 2022}
      {Autonomous University of Madrid · OBERAXE (State Secretariat for Migration)}{Madrid, Spain}
      \resumeItemListStart
        \resumeItem{Part of \href{https://real-up.eu/summary-in-english/}{\textcolor{BlueViolet}{REAL-UP, Combating Hate Speech Project}} approved by the Citizens, Equality, Rights and Values Programme (CERV) of the European Commission under the Call: CERV-2021-EQUAL.}
        \resumeItem{Design and implementation of the main hate speech algorithm for the improvement of an IT tool developed for the Spanish Government.}
        \resumeItem{Creation of automatic processes for detecting hate speech beyond Twitter.}
      \resumeItemListEnd

      \resumeSubheading
      {R\&D Tax Consultant Intern}{October 2019 -- March 2020}
      {KPMG Spain}{Madrid, Spain}
      \resumeItemListStart
        \resumeItem{Drafting scientific and technological descriptions of AI projects.}
        \resumeItem{Automatizing spreadsheets for the value of claims, apportioned between the different R\&D regimes.}
        \resumeItem{Explored ways to analyse and present relevant financial information to support R\&D tax credit claims.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/glorelvalle/socialhaterbert}{\textbf{SocialHaterBERT}} · \emph{Bachelor's Thesis}}{September 2020 -- June 2021}
          \resumeItemListStart
            \resumeItem{Main title of \textit{Detecting hate speech messages on Twitter: a study based on social network profiles.}}
            \resumeItem{Conducted in cooperation with the Spanish National Office Against Hate Crimes of the Spanish State Secretariat for Security (Ministry of Interior).}
            \resumeItem{Proposal for a novel NLP approach for feature analysis based on user profiles, related social environment and generated tweets.}
            \resumeItem{Development of a combined BERT-based model capable of analyzing features beyond those intrinsically lie in the text for the detection of hate speech on Twitter.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------Courses-----------
\section{Courses and Certificates}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {}{}\\
          \vspace{-0.4em}
          %{\textbf{Reinforcement Learning Specialization (1/4)} · \emph{University of Alberta}}{ \hspace{10.6em} July 2022}\\
          %\vspace{0.3em}
          {\textbf{IBM Data Science Professional Certificate (3/10)} · \emph{IBM}}{ \hspace{15.3em} July 2021}\\
          \vspace{0.3em}
          {\textbf{Python for Data Science} · \emph{Coursera Project Network}}{ \hspace{18.5em} July 2020}\\
          \vspace{0.3em}
          {\textbf{Natural Language Processing} · \emph{National Research University Higher School of Economics }}{ \hspace{0.5em} August 2019} \\
          \vspace{0.3em}
          {\textbf{Applied Text Mining in Python} · \emph{University of Michigan}}{ \hspace{16em} June 2019}\\
  
          
          
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Publications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Articles in conference proceedings}}{ }
          
          \resumeItemListStart
          \resumeItem{del Valle, G. \& Quijano-Sánchez, L.\& Gómez, J., \emph{Detecting Hate Messages on Twitter: A BERT-based Model for the Classification of Hate Speech in Spanish}, in Proceedings of International Congress "Hate and Discrimination in turbulent times", 2021, Málaga, Spain.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%%-----------PROJECTS-----------
\section{Awards and achievements}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{Finalist at European Crime Prevention Award and Best Practice Conference (\textcolor{BlueViolet}{\href{https://eucpn.org/service/bpc-ecpa}{BPC-ECPA})} }}{October 2021}
      
      \resumeItemListStart
        \resumeItem{Entry: \textcolor{BlueViolet}{\href{https://eucpn.org/document/socialhaterbert-automatic-detection-and-monitoring-of-hate-speech-on-twitter-through-a}{SocialHaterBERT: automatic detection and monitoring of hate speech on Twitter through a dichotomous approach based on textual analysis and user profiles.}}}
        \resumeItem{Winner of the internal selection process in Spain.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Advanced}\hspace{1em}
     \textbf{Spanish}{: Native}\hspace{1em}
     \textbf{French}{: Elementary} 
    }}
 \end{itemize}


%-------------------------------------------

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Advanced knowledge}{: Python, C, \LaTeX, SQL, Neo4j, NLP Transformers.} \\
     \textbf{Intermediate knowledge}{: C++, R, Lisp, Java, Swift, HTML/CSS, JavaScript, MongoDB.}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
