%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\usepackage{fontawesome}
\usepackage{academicons}
\usepackage{hyperref}

\hypersetup{colorlinks,urlcolor=BlueViolet,linkcolor=BlueViolet}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin = 0.15in, label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Gloria del Valle Cano} \\ \vspace{0.9em}
    \href{tel:+34635886867}{\raisebox{-0.05\height}\faMobile\ } · \href{mailto:glorelvalle@gmail.com}{\raisebox{-0.05\height}\faEnvelope\ } ·
    \href{https://github.com/glorelvalle}{\raisebox{-0.05\height}\faGithub\ } ·
    \href{https://glorelvalle.github.io}{\raisebox{-0.05\height}\faGlobe\ } ·
    \href{https://linkedin.com/in/glorelvalle}{\raisebox{-0.05\height}\faLinkedin\ } ·
    \href{https://scholar.google.es/citations?user=qtELGLwAAAAJ&hl=es&oi=ao}{\faGraduationCap}
\end{center}

\vspace{0.1em}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\normalsize Data Scientist \small @ \textit{Menhir AI}}{ \small \textcolor{Gray}{02/2023 -- \textit{Present}}}{}{}
        \small I performed Real Estate decision-making algorithms. CI/CD of AI models and automation processes.
      \resumeSubheading
      {\normalsize Data Scientist \small @ \textit{Grupo TRC}}{ \small \textcolor{Gray}{09/2022 -- 02/2023}}{}{}
        \small I designed Speech-to-Text and Text-to-Speech models (\emph{transformers}) for Interactive Voice Response systems. I also participated in the development of Computer Vision and biometrics models for a security project with drones.

      \resumeSubheading
      {\normalsize Research Assistant \small @ \textit{Autonomous University of Madrid}}{\small \textcolor{Gray}{01/2022 -- 09/2022}}
        \scriptsize \textup{I designed and developed the main hate speech algorithm for the Spanish Government and created automatic processes for detecting hate patterns beyond social media. Part of \href{https://real-up.eu/summary-in-english/}{REAL-UP, Combating Hate Speech Project}, in collaboration with OBERAXE (State Secretariat for Migration).}
      
      \resumeSubheading
      {\normalsize R\&D Consultant Intern \small @ \textit{KPMG Spain}}{ \small \textcolor{Gray}{10/2019 -- 03/2020}}
        \scriptsize \textup{Along with my colleagues, I participated in several AI projects where I explored ways to analyse and manipulate relevant financial information to support R\&D regimes.}
    \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
    %\resumeSubHeadingListStart
          \resumeItemListStart
              \resumeItem{\href{https://doi.org/10.1016/j.eswa.2022.119446}{SocialHaterBERT: A dichotomous approach for automatically detecting hate speech on Twitter}{\hspace{8.26em} \textcolor{Gray}{2023}} \\ \href{https://doi.org/10.1016/j.eswa.2022.119446}{through textual analysis and user profiles.} \\ \scriptsize \textbf{Valle-Cano, G.} Quijano-Sánchez, L. Liberatore, F. \& Gómez, J. \textcolor{Gray}{Expert Systems With Applications (ESWA).}}
              \resumeItem{\href{https://dialnet.unirioja.es/servlet/articulo?codigo=8653016}{Detecting Hate Messages on Twitter: A BERT-based Model for the Classification of Hate Speech in Spanish}{\hspace{3em}\textcolor{Gray}{2021}} \\ \scriptsize \textbf{Valle-Cano, G.} Quijano-Sánchez, L. \& Gómez, J. \textcolor{Gray}{Proceedings of the International Congress \emph{Hate and Discrimination in Turbulent Times}.}}
          \resumeItemListEnd
   % \resumeSubHeadingListEnd
    
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MSc Data Science \small @ \textit{Autonomous University of Madrid}}{\small \textcolor{Gray}{09/2021 -- 06/2023}}{}{}
      \small Studying Advanced Methods in Statistics, Stochastic Processes, Bayesian Methods and Functional Methods, inter alia.
         
        
    \resumeSubheading
      {\normalsize BSc Computer Science Engineering \small @ \textit{Autonomous University of Madrid}}{\small \textcolor{Gray}{09/2013 -- 06/2021}}{}{}
      \small Studying solutions based on ML, Software Engineering, Database Fundamentals and Complex Algorithms, inter alia. \\ During my studies, I worked in part-time jobs as sales assistant (25-35 hours per week).
    
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/glorelvalle/socialhaterbert}{\textbf{SocialHaterBERT}} · \textbf{\textcolor{Gray}{\emph{Bachelor's Thesis}} · [Grade A]}}{\textcolor{Gray}{\small 09/2020 -- 06/2021}}
          {\scriptsize \textup{A proposal for a combined \textbf{BERT-based model} for \textbf{hate speech detection}, capable of going further with the features lying in the text. I developed \textbf{NLP models} to make a user profile analysis, with its related social environment (\textbf{Graph Theory} and \textbf{Neo4j}) and generated tweets (\textbf{Twitter API}). Conducted in cooperation with the Spanish National Office Against Hate Crimes of the \textbf{Ministry of Interior}. \newline This gave me the opportunity to participate in \href{https://eucpn.org/service/bpc-ecpa}{European Crime Prevention Award and Best Practice Conference (BPC-ECPA)} where I was able to represent Spain with the \href{https://eucpn.org/document/socialhaterbert-automatic-detection-and-monitoring-of-hate-speech-on-twitter-through-a}{SocialHaterBERT project applied to cyberbullying.}}}{}
    \resumeSubHeadingListEnd


%-----------Courses-----------
\section{Courses}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          %{\textbf{Reinforcement Learning Specialization (1/4)} · \emph{University of Alberta}}{ \hspace{10.6em} July 2022}\\
          %\vspace{0.3em}
          %{\textbf{IBM Data Science Professional Certificate (3/10)} · \emph{IBM}}{ \hspace{15.3em} July 2021}\\
          %\vspace{0.3em}
          %{\textbf{Python for Data Science} · \emph{Coursera Project Network}}{ \hspace{18.5em} July 2020}\\
          %\vspace{0.3em}
          {\textbf{\small Natural Language Processing} · \small \emph{National Research University Higher School of Economics }}{ \hspace{6.8em} \small \textcolor{Gray}{08/2019}} \\
          \vspace{0.2em}
          {\textbf{\small Applied Text Mining in Python} · \small \emph{University of Michigan}}{ \hspace{19.6em} \small \textcolor{Gray}{06/2019}}\\
    \resumeSubHeadingListEnd
    
%-----------LANGUAGES-----------
%\section{Languages}
% \begin{itemize}[leftmargin=0.15in, label={}]
%    \small{\item{
%     \textbf{English}{: Advanced}\hspace{1em}
%     \textbf{Spanish}{: Native}\hspace{1em}
%     \textbf{French}{: Elementary} 
%    }}
% \end{itemize}


%-------------------------------------------

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Advanced knowledge}{: Python, C, \LaTeX, SQL, Neo4j, NLP, Transformers, Neptune AI.} \\
     \textbf{Intermediate knowledge}{: C++, R, Lisp, Java, Swift, HTML/CSS, JavaScript, MongoDB, ArangoDB, Kubernetes.} \\
     \textbf{Languages}{: English (\textit{Advanced}), Spanish (\textit{Native}), French (\textit{Elementary})}.
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
